\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-01-23 doc/USER_MANUAL/02_getting_started.tex
added Daniel Peter's instructions for CUDA8

>>>>

When compiling for GPU cards i.e. using CUDA, you can use:

\texttt{./configure --with-cuda}

for CUDA version 4, or

\texttt{./configure --with-cuda=cuda5}

for CUDA version 5, or

\texttt{./configure --with-cuda=cuda6}

for CUDA version 6, or

\texttt{./configure --with-cuda=cuda8}

for CUDA version 8.

Before CUDA version 5, one version supported basically one new architecture and needed a different kind of compilation.
Since version 5, the compilation has stayed the same, but newer versions supported newer architectures.
However at the moment, we still have one version linked to one specific architecture:

- CUDA 4 for Fermi,
- CUDA 5 for Tesla K20
- CUDA 6 for Tesla K80
- CUDA 8 for Pascal P100.

So even if you have the new CUDA toolkit version 8, but you want to run on say a K20 GPU, then you would still configure with:

\texttt{./configure --with-cuda=cuda5}

The compilation should work and the cuda5 setting chooses the right architecture (-gencode=arch=compute\_35,code=sm\_35 for K20 cards).

So, type

\texttt{./configure --with-cuda=cuda8}

for Pascal P100 boards.
